Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2017-09-13 Paper/Manuscript.tex
Bug

This is potentially an important result that sheds light on the globalization processes.
However, that result is actually driven by an \textit{ad hoc} method of aggregation that captures structure effects.
The authors use an end-of-period GDP arithmetic average of bilateral transport costs to compute country-specific trade costs. In a simple symmetric three-country model, we show that this is the equivalent to weighting the information given by each dyadic trade flow by the product of end-of-period GDP. and the value of the trade flow to the power $1/(1-\sigma)$  (with \sigma, as discussed latter, > 1).
In contrast, a theoretically justified method weights, more naturally, the information given by each dyadic trade flow by the the value of the trade flow. 
Because $1/(1-\sigma)$ < 0, this means among other things that the importance of small dyadic trade flows in the computation of country-specific trade costs is too large in the authors' computations. Their conclusion on the difference between the two globalization comes from the fact that the dyads with the fastest growing trade in the first wave of globalization start with very small trade and this this is not the case in the second wave of globalization.

>>>>

This is potentially an important result that sheds light on the globalization processes.
However, that result is actually driven by an \textit{ad hoc} method of aggregation that captures structure effects.
The authors use an weighted arithmetic average of bilateral transport costs to compute country-specific trade costs. Putting aside the weight, in a simple symmetric three-country model, we show that this is the equivalent to using a power or generalized mean with exponent $1/(1-\sigma)$ on the value of dyadic trade flows.
In contrast, a theoretically justified method would use a simple arithmetic mean of the value of the dyadic trade flow. 
Because $1/(1-\sigma)$ < 0, this means among other things that the importance of small dyadic trade flows in the computation of country-specific trade costs is too large in the authors' computations.
This is not compensated by the weight they use (end-of-period GDP).
Their conclusion on the difference between the two globalization comes from the fact that the dyads with the fastest growing trade in the first wave of globalization start with very small trade and this this is not the case in the second wave of globalization.
